CSCI 447: Project 1

### 2019-09-13 paper/paper.tex
paper progress

\section{Problem Statement}
Given a data set of which all the correct classifications are known, we can implement and execute a training algorithm on a subset of the data. Then, once trained, the algorithm will guess the classes of another subset of the data and measure the performance. For this assignment, we were provided with 5 real-world data sets. Our task was to implement a training algorithm and guess classifications for each of these 5 data sets and then utilize two different loss functions to measure the accuracy and performance of our predictions. We ran this algorithm on the original versions of each data set, and then introduced noise to each of the data sets by shuffling attribute values among 10\% of the values, and ran the algorithm of the five shuffled versions of the data. We hypothesized that we would acheive

>>>>

\section{Problem Statement}
Given a data set of which all the correct classifications are known, we can implement and execute a training algorithm on a subset of the data. Then, once trained, the algorithm will guess the classes of another subset of the data and measure the performance. For this assignment, we were provided with 5 real-world data sets. Our task was to implement a training algorithm and guess classifications for each of these 5 data sets and then utilize two different loss functions to measure the accuracy and performance of our predictions. We ran this algorithm on the original versions of each data set, and then introduced noise to each of the data sets by shuffling attribute values among 10\% of the values, and ran the algorithm of the five shuffled versions of the data. \\ \\
% Hypotheses
Our hypotheses for each data set are as follows: \\

\textit{Breast Cancer Wisconsin:} This data set is comprised of 9 quantitative variables, and each data example can be classified as either benign or malignant. We hypothesized that, given that there are only two possible classifications, that we will acheive no less than 85\% accuracy (i.e. a 0-1 loss score of 0.75) on our unshuffled data. \\ \\
\textit{Glass:} This data set is comprised of 7 quantitative variables, and each data example can be classified as one of 7 possible glass types: building\_windows\_float\_processed, building\_windows\_non\_float\_processed, vehicle\_windows\_float\_processed, vehicle\_windows\_non\_float\_processed, containers, tableware, or headlamps. We hypothesize that we will achieve no less that 65\% accuracy for this data set, given that there are 7 potential classes. \\ \\
\textit{Iris:} This dataset is comprised of 4 quantitative variables. Each data example can be classified as one of three different flower types. We are predicting approximately 75\% accuracy. \\ \\
\textit{Soybean:} This dataset is comprised of 35 attributes, and each data example can be classified as one of four different classifiers. We hypothesize 70\% accuracy for this data set. \\ \\
\textit{Voting Records:} This data set is comprised \\
